Unit tests

### 2018-03-08 Tests.Rmd
checking Pbds filled in

<!--Test the cor stat-->
```{r test_copula_function_flexible_cor, echo=T}
#Test the cor stat
source("CopulaFunctions_flexible.R")

h<-Corbds(vi,vj,lb=.05,ub=.45)
inds<-1:4
ht<-sum((vi[inds]-mean(vi))*(vj[inds]-mean(vj)))/((length(vi)-1)*sqrt(var(vi)*var(vj)))

if (abs(h-ht)<1e-12)
{
  prin("passed")
}
```

<!--Test the D2 stat-->
```{r test_copula_function_flexible_D2, echo=T}
#Test the D2 stat
source("CopulaFunctions_flexible.R")

h<-D2bds(vi,vj,lb=.05,ub=.45)
if (abs(sum(ep[1:4]^2)/2-h)<1e-12)
{
  print("passed")
}
```

<!--Test the P stat-->
```{r test_copula_function_flexible_P, echo=T}
#Test the P stat
source("CopulaFunctions_flexible.R")

#Shya to write, see above to get an idea of what kind of test we need
```

>>>>

```{r plot_vivj,echo=T}
plot_vivj<-function(vi,vj,lb,ub){
 plot(vi,vj,col="red",xlim=c(0,1),ylim=c(0,1),asp=1,cex.axis=0.5)
 axis(1, at = seq(0, 1, by = 0.1),cex.axis=0.5)
 abline(a=2*lb,b=-1,col="blue")
 abline(a=2*ub,b=-1,col="green4")
 abline(a=0,b=1)
 rect(0,0,1,1)
}
```

<!--Test the cor stat-->
```{r test_copula_function_flexible_cor, echo=T}
#Test the cor stat
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
h<-Corbds(vi,vj,lb=lb,ub=ub)
inds<-1:4
ht<-sum((vi[inds]-mean(vi))*(vj[inds]-mean(vj)))/((length(vi)-1)*sqrt(var(vi)*var(vj)))

if (abs(h-ht)<1e-12)
{
  print("passed")
}
```

<!--Test the D2 stat-->
```{r test_copula_function_flexible_D2, echo=T}
#Test the D2 stat
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
h<-D2bds(vi,vj,lb=lb,ub=ub)
if (abs((sum(ep[1:4]^2)/2)-h)<1e-12)
{
  print("passed")
}
```

<!--Test the P stat-->
```{r test_copula_function_flexible_P, echo=T}
#Test the P stat
source("CopulaFunctions_flexible.R")
lb=0
ub=.45
vi<-c(vi[3],vi[7],vi[9])
vj<-c(vj[3],vj[7],vj[9])

# When two parallel boundary line are on the left side of vi+vj=1 line

#(vi,vj) plot in unit box : lower tail
plot_vivj(vi=vi,vj=vj,lb=lb,ub=ub)

#calling P stat for lower tail
hl<-Pbds(vi,vj,lb=lb,ub=ub)

#plot the step fn
plot(hl$dist_S,hl$S,type="b")

#calculate the area under the curve 
vertices<-unique(hl$dist_S[(hl$dist_S!=0)])
area_S<-(vertices[2]-vertices[1])*1
area_S

area_S==hl$Au_S # it's a check

hl$Au_Si

#P stat value for lower tail
(area_S-hl$Au_Si)==hl$abs_res

# When two parallel boundary line are on the right side of vi+vj=1 line
lb=0
ub=.4 # if ub=0.45 then hu$Au_Si = hl$Au_Si : so, it's a check on Au_Si
#(vi,vj) plot in unit box : upper tail
plot_vivj(vi=vi,vj=vj,lb=(1-ub),ub=(1-lb))

#calling P stat for upper tail
hu<-Pbds(vi,vj,lb=(1-ub),ub=(1-lb))

#plot the step fn
plot(hu$dist_S,hu$S,type="b")

#calculate the area under the curve 
w1<-unique(hu$dist_S[(hu$dist_S!=0)])
w1  #x-coord where the jump occurs
h1<-unique(hu$S)
h1  #y-coord where the jump occurs
area_S<-((w1[2]-w1[1])*(h1[2]-h1[1]))+((w1[3]-w1[2])*(h1[3]-h1[1]))
area_S

area_S==hu$Au_S  # it's a check

hu$Au_Si

#P stat value for upper tail
(area_S-hu$Au_Si)==hu$abs_res

# When two parallel boundary lines are on either side of vi+vj=1 line
lb=0.3
ub=0.8

#calling P stat for middle section
hm<-Pbds(vi,vj,lb=lb,ub=ub)

#(vi,vj) plot in unit box : middle section
plot_vivj(vi=vi,vj=vj,lb=lb,ub=ub)

#plot the step fn
plot(hm$dist_S,hm$S,type="b")

#calculate the area under the curve 
w1<-unique(hm$dist_S[(hm$dist_S!=0)])
w1  #x-coord where the jump occurs
h1<-unique(hm$S)
h1  #y-coord where the jump occurs
area_S<-((w1[2]-w1[1])*(h1[2]-h1[1]))+((w1[3]-w1[2])*(h1[3]-h1[1]))
area_S

area_S==hm$Au_S # it's a check

hm$Au_Si

#P stat value for middle section
(area_S-hm$Au_Si)==hm$abs_res
```
